\documentclass[sigconf]{acmart}

\usepackage{booktabs} % For formal tables


\begin{document}
\title{Visualizing User Behavior on the Places and Spaces Website}

\author{Avadhoot Agasti}
\affiliation{School of Informatics and Computing, Bloomington, IN 47408, U.S.A.}
\email{aagasti@indiana.edu}

\author{Sharad Ghule}
\affiliation{School of Informatics and Computing, Bloomington, IN 47408, U.S.A.}
\email{ssghule@iu.edu}

\author{Shreyas Rewagad}
\affiliation{School of Informatics and Computing, Bloomington, IN 47408, U.S.A.}
\email{srewagad@iu.edu}

\author{Leonard Mwangi}
\affiliation{School of Informatics and Computing, Bloomington, IN 47408, U.S.A.}
\email{lmwangi@indiana.edu}


\begin{abstract}

The \textit{Places and Spaces: Mapping Science} exhibit introduces science mapping techniques to the general public and to experts across disciplines for educational, scientific, and practical purposes. The exhibit website \textit{www.scimaps.org} provides information about people behind the exhibit; showcases maps and macroscopes; lists past, present and planned exhibit venues and dates. The website underwent a redesign in 2015 to update the organization and user interface of the website and this study aims to analyze and visualize the changes in behaviour of users of the website due to the redesign. After scraping raw data off of monthly website usage reports in HTML format and cleaning and trasnforming it into usable format, Tableau was used to create an interactive dashboard that would allow a user to gather insights from a number of visualizations. The dashboard allows a user to analyze the data from a high level as well as to drill down into details if required. Several interesting insights that were uncovered using the dashboard are presented.
\end{abstract}


\keywords{Tableau, Visualization, Geospatial, URL, Hits, Pageviews, Parsing, Web Analytics, Line Graph, Tree Map, Dynamic Visualization}

\maketitle

\input{introduction}
\input{requirements}
\input{technicalsolution}

\input{visualizations}
\input{viz_top_countries}
\input{viz_top_agents}
\input{viz_top_refs}
\input{viz_top_searches}
\input{viz_top_urls}
\input{viz_events_traffic}
\input{viz_dashboard}

\input{keyinsights}

\input{similartechnologies}

\input{conclusion}

%\end{document}  % This is where a 'short' article might terminate



\appendix
%Appendix A
\section{Work Distribution}
The co-authors of this report worked together on the design of technical
solutions, visualizations, implementation and documentation. Specifially,
below given is the work distribution
\begin{itemize}
\item Avadhoot Agasti
    \begin{itemize}
    \item Team lead and overall coordination.
    \item Data parser implementation.
    \item Visualization of top searches.
    \item Putting together latext template for report writing.
    \item Writing section \ref{techsol} and section \ref{viztopsearches}
     in this
    report.
    \end{itemize}

\item Sharad Ghule
    \begin{itemize}
    \item Visualization of top countries
    \item Visualization of events and website traffic coorelation
    \item Helping with intermediate deliverables
    \item Writing Abstract, section \ref{intro}, section \ref{requirements},
    section \ref{vizevents} and
    section \ref{vizcountries}  in this report.
    \end{itemize}

\item Shreyas Rewagad
    \begin{itemize}
    \item Visualization of top agents
    \item Visualization of most popular URLs
    \item Research on other similar technologies
    \item Writing section \ref{viztopagents}, section \ref{viz_top_urls} and
    section \ref{similartech}  in this report.
    \end{itemize}

\item Leonard Mwangi
    \begin{itemize}
    \item Visualization of top referrals
    \item Visualization of overall statistics
    \item Creating dashboard
    \item Writing section \ref{viztoprefs}, section \ref{viz_dashboard} and
    section \ref{keyinsights} in this report.
    \end{itemize}

\end{itemize}


\section{Acknowledgements}
 The authors thank Prof. Katy Borner for her technical guidance. The
 authors would also like to thank TAs of Information Visualization class for their valued
 support.


\bibliographystyle{ACM-Reference-Format}
\bibliography{main} 

\end{document}
