\section{Other Similar Technologies} \label{similartech}
There are various performance parameters and aspects that aren’t reviewed in the current paper due to unavailability of data. A good web analysis done by mining the user data would yields insights that could boost website traffic and potential business advancements. In this internet age the delivery of such Key Performance Indicators and solutions need to be real-time.  In this section we review some of the tools that could help in web analysis. 

\subsection{Google Analytics}
This is a freeware made by Google to monitor and report website traffic. The tool showcases the descriptive statistics of the website on high-level. We can also procure intricate details and visualize the trend in user behavior pattern across the webpages. Apart from the fine grained details, the tool possesses Google intelligence and Google’s proprietary machine learning library integration. Thus making the Website owner aware of the possible actions that could potentially increase in website traffic. In order to link the tool to the website a tracking code is added to the web pages, this essentially integrates Google analytic in your website. This is also bundled along with other Google services which would help monitor the website via mobile devices.

\subsection{Piwik}
Piwik is a free open-source utility tool that can help the owner analyze the website traffic and determine the performance of various content hosted. Over the years users have added myriad plugins to Piwik to perform in detailed analysis and user profiling of the website traffic. This coupled with mobile integration helps the owner monitor the website traffic.
